An Improved ANS Transaction Template

### 2018-01-27 paper.tex
formating, cleaning

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Theory}

Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots
Some text for introduction etc\ldots

\section{Cascade Enrich Construction}
\subsection{Centrifuge properties}
The present work uses the analytical solution by R\"aetz \cite{ref} of the
differential equation for the gas centrifuge as described in \cite{Glaser2008}. Centrifuge parameters, such as average gas temperature, rotation speed, height, feed flow rate, diameter, pressure ratio,
counter-current flow ratio, and efficiency have been chosen to match the cascade design
describe in \cite{glaser2008} and \cite{Walker2017}. These parameters for a P1-type centrifuge are used to estimate the JCPOA-compliant IR-1 centrifuge.

@@

The cascade is built to be ideal, defined by $\alpha =\beta = const$
for all stage of the cascade, where $\alpha$ and $\beta$ respectively represent
the feed to product and the feed to tail enrichment factors.
$\alpha$ can be expressed as a function of the feed rate $F$, the separative performance $\delta U(\theta)$ and $\theta$,
and $\beta$ as a function of $alpha$ and $\theta$:
\begin{subequations} \label{eqs:alphabeta}
    \begin{equation} \label{eq:alpha}
    \alpha = \sqrt{\frac{2\delta U}{F} \frac{1-\theta}{\theta}}+1
\end{equation}
\\
\begin{equation}\label{eq:beta}
    \beta = R
              \dfrac{1 - \dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1 - \theta}}
                   {\dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1 - \theta}}
\end{equation}
\end{subequations}

@@

The design of the cascade is performed through 2 steps. First one determines the
configuration and number of stages, adding stages following the previously
described procedure, until $N'_{last} > N'_{requested}$ and $N''_{last} <
N''_{requested}$. (Note that $N'_{last}$ corresponds to the product assay of the
last enrichment stage, and $N''_{last}$ to the tail assay of the last stripping
stage). This allows to determine the number of enriching and stripping stages as
well as their enrichment properties ($N_{i}$, $N'_{i}$,
$N''_{i}$,$\theta_{i}$i).
% might be more useful to the reader to say this in words instead of variables, i.e. adding stages until the product assay of the final stage is greater than or equal to than the desired assay, and the tails assay is similarly less than or equal to the desired tails assay

The second step determines how to populate the cascade with the user-defined maximum number of centrifuges. One first solves the linear flow equation to determine the theoretical flow in the
cascade:
\begin{strip}
\begin{equation}
\setcounter{MaxMatrixCols}{20}
\begin{bmatrix}
-1         & 1-\theta_{S+1} & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
\theta_{S} & -1             & 1-\theta_{S+2} & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
0          & 0              & 0              & 0 & ... & 0 & \theta_{-1}  & -1  & 1 - \theta_{1} & 0 & ... & 0            & 0            & 0 \\
           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & \theta_{E-2} & -1           & 1-\theta_{E} \\
0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & \theta_{E-1} & -1
\end{bmatrix}
\times
\begin{bmatrix}
     F_{S}   \\
     F_{S+1} \\
     \cdots  \\
     F_{0}   \\
    \cdots   \\
    F_{E-1}  \\
    F_{E}
\end{bmatrix}
=
\begin{bmatrix}
     0   \\
     0 \\
     \cdots  \\
     F   \\
    \cdots   \\
    0  \\
    0
\end{bmatrix}
%\caption{caption needed!}
\label{eq:flow}
\end{equation}
\end{strip}
Once the relative flow of each stage, $F_{i}$, has been determined, the
cascade can be populated with actual machines up the stages
until either the maximum number available of machines or the maximum feed
flow is reached.

@@

\subsection{Explored Cases}
\subsubsection{Reference Case}
The reference case corresponds to the most ideal cascade design--utilizing all of the 5060
centrifuges available within JCPOA to produce an enriched product at $>90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assays are respectively
0.0071/0.903/0.0028.
%maybe include some cascade shape figures?

\subsubsection{Case 1}
The case 1 is designed to configure 30 cascades in the scenario (the maximum allowable under
the JCPOA agreement), all designed the same way. The basic properties are:\\
- less than 169 centrifuges per cascade,\\
- F/P/T assays: 0.0071/0.035/0.003.\\
The corresponding design is:\\
- 167 centrifuges,\\
- F/P/T assays: 0.0071/0.0412842/0.00290548.\\

\subsubsection{Case 2} Case 2 also limited to 30 cascades in the scenario (the
maximum allowable under the JCPOA agreement), but this time each level of
cascades are designed to take feed from the previous level's product. Each
cascade has 4 stripping stages and 10 enriching stages. The configuration of
cascade levels can be found in table \ref{tab:cascadelvl}. Unlike case 1, the
organization of centrifuges varies from level to level. Each level is re-optimized
to have the most efficient number of centrifuges in each stage, although the total number
of stages remains constant. T

 %we haven't defined a level

@@

\subsection{Level optimization}
A last round of optimization if then ran in order to limit the number of cascade
level to the amount of level required produce HEU, and then to populate the
different level with a total of 30 cascades in order to maximize the HEU
production rate.

\section{Results}
\subsection{Enrichment}
\subsubsection{Without tail recycling}
Despite the reconfiguration of each level occurring in the second case, the case
1 is notably more effective in producing HEU than case 1. Indeed, as observed in Figure
\ref{fig:assay_c1_rc} and \ref{fig:assay_c2_rc}, the first case is able to
produce an uranium product enrich at $98\%$ while the second case is only able
to reach an enrichment of $88.3\%$ with the same number of levels.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 without recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c1_nr}
\end{figure}
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_2_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 2 without recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c2_nr}
\end{figure}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 with recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c1_r}
\end{figure}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_2_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 2 with recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c2_r}
\end{figure}

@@

The included ANS style file and this clear example file are a panacea for
the hours of headache that invariably results from formatting a document in
Microsoft Word.

>>>>

\section{Cascade Enrich Construction}
\subsection{Centrifuge properties}

The present work uses the analytical solution by R\"aetz \cite{ref} of the
differential equation for the gas centrifuge as described in \cite{Glaser2008}.
Centrifuge parameters, such as average gas temperature, rotation speed, height,
feed flow rate, diameter, pressure ratio, counter-current flow ratio, and
efficiency have been chosen to match the cascade design describe in
\cite{glaser2008} and \cite{Walker2017}. These parameters for a P1-type
centrifuge are used to estimate the JCPOA-compliant IR-1 centrifuge.

@@

The cascade is built to be ideal, defined by $\alpha =\beta = const$ for all
stage of the cascade, where $\alpha$ and $\beta$ respectively represent the feed
to product and the feed to tail enrichment factors.  $\alpha$ can be expressed
as a function of the feed rate $F$, the separative performance $\delta
U(\theta)$ and $\theta$, and $\beta$ as a function of $alpha$ and $\theta$:

\begin{subequations} \label{eqs:alphabeta}
    \begin{equation} \label{eq:alpha}
    \alpha = \sqrt{\frac{2\delta U}{F} \frac{1-\theta}{\theta}}+1
\end{equation}
\\
\begin{equation}\label{eq:beta}
    \beta = R
              \dfrac{1 - \dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1 - \theta}}
                   {\dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1 - \theta}}
\end{equation}
\end{subequations}

@@

The design of the cascade is performed through 2 steps. First one determines the
configuration and number of stages, adding stages following the previously
described procedure, until $N'_{last} > N'_{requested}$ and $N''_{last} <
N''_{requested}$. (Note that $N'_{last}$ corresponds to the product assay of the
last enrichment stage, and $N''_{last}$ to the tail assay of the last stripping
stage). This allows to determine the number of enriching and stripping stages as
well as their enrichment properties ($N_{i}$, $N'_{i}$,
$N''_{i}$,$\theta_{i}$i).
% might be more useful to the reader to say this in words instead of variables,
% i.e. adding stages until the product assay of the final stage is greater than
% or equal to than the desired assay, and the tails assay is similarly less than
% or equal to the desired tails assay

The second step determines how to populate the cascade with the user-defined
maximum number of centrifuges. One first solves the linear flow equation to
determine the theoretical flow in the cascade:

\begin{strip}
\begin{equation}
\setcounter{MaxMatrixCols}{20}
\begin{bmatrix}
-1         & 1-\theta_{S+1} & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
\theta_{S} & -1             & 1-\theta_{S+2} & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
0          & 0              & 0              & 0 & ... & 0 & \theta_{-1}  & -1  & 1 - \theta_{1} & 0 & ... & 0            & 0            & 0 \\
           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & \theta_{E-2} & -1           & 1-\theta_{E} \\
0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & \theta_{E-1} & -1
\end{bmatrix}
\times
\begin{bmatrix}
     F_{S}   \\
     F_{S+1} \\
     \cdots  \\
     F_{0}   \\
    \cdots   \\
    F_{E-1}  \\
    F_{E}
\end{bmatrix}
=
\begin{bmatrix}
     0   \\
     0 \\
     \cdots  \\
     F   \\
    \cdots   \\
    0  \\
    0
\end{bmatrix}
%\caption{caption needed!}
\label{eq:flow}
\end{equation}
\end{strip}
Once the relative flow of each stage, $F_{i}$, has been determined, the
cascade can be populated with actual machines up the stages
until either the maximum number available of machines or the maximum feed
flow is reached.

@@

\subsection{Explored Cases}
\subsubsection{Reference Case}

The reference case corresponds to the most ideal cascade design--utilizing all
of the 5060 centrifuges available within JCPOA to produce an enriched product at
$>90\%$ of U-235, stripping the tail product up to 0.28 $\%$ from a feed of
natural uranium.  The design cascade in this case, includes 4 stripping stages,
and 38 enriching stages. The Feed/Product/Tail (F/P/T) assays are respectively
0.0071/0.903/0.0028.

\subsubsection{Case 1}

The case 1 is designed to configure 30 cascades in the scenario (the maximum
allowable under the JCPOA agreement), all designed the same way. The basic
properties are: less than 169 centrifuges per cascade, F/P/T assays of
0.0071/0.035/0.003. The corresponding design includes 167 centrifuges, with
respective F/P/T assays of 0.0071/0.0412842/0.00290548.

\subsubsection{Case 2}

Case 2 also limited to 30 cascades in the scenario (the maximum allowable under
the JCPOA agreement), but this time each level of cascades are designed to take
feed from the previous level's product. Each cascade has 4 stripping stages and
10 enriching stages.

@@

The configuration of cascade levels can be found in table
\ref{tab:cascadelvl}. Unlike case 1, the organization of centrifuges varies from
level to level. Each level is re-optimized to have the most efficient number of
centrifuges in each stage, although the total number of stages remains constant.

\subsection{Level optimization}

A last round of optimization if then ran in order to limit the number of cascade
level to the amount of level required produce HEU, and then to populate the
different level with a total of 30 cascades in order to maximize the HEU
production rate.

\section{Results}
\subsection{Enrichment}
\subsubsection{Without tail recycling}

Despite the reconfiguration of each level occurring in the second case, the case
1 is notably more effective in producing HEU than case 1. Indeed, as observed in
Figure \ref{fig:assay_c1_rc} and \ref{fig:assay_c2_rc}, the first case is able
to produce an uranium product enrich at $98\%$ while the second case is only
able to reach an enrichment of $88.3\%$ with the same number of levels.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 without recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c1_nr}
\end{figure}
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_2_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 2 without recycling. }\label{fig:assay_c2_nr}
\end{figure}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 with recycling. }\label{fig:assay_c1_r}
\end{figure}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_2_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 2 with recycling.}\label{fig:assay_c2_r}
\end{figure}

@@

Where the JCPOA aggrement
